Naturalness and Long-lived Beyond the Standard Model Particles

### 2017-07-28 tex/draft.tex
Edit CMS detector

\usepackage[final]{fixme}
\fxsetup{layout=footnote}
\usepackage[left]{lineno}
\usepackage{amsmath,amsthm,amssymb,mathtools,graphicx,caption,subcaption,mathrsfs,cancel,multirow,enumitem,setspace,sectsty,cite,hyperref,siunitx}
\usepackage{fullpage}

@@

    All massive particles correct the Higgs mass with terms proportional to $\Lambda^2$. Experimentally, the Higgs mass is \SI{125}{GeV}\fxnote{cite CMS, ATLAS}, a value that must be achieved by the sum of the bare mass and all corrections. Although corrections differ in sign, the precise cancellation of many extremely large terms to produce a value as small as the Higgs mass is extremely unlikely. In fact, the fine-tuning necessary to produce the Higgs mass is on the order of one part in \num{e30} if the SM is valid up to the Plank scale ($\mPlanck\approx$ \SI{e16}{GeV}), where quantum gravity becomes important. While it's possible that the bare mass and corrections just so happen to almost perfectly cancel, such miraculous fine tuning could also be a hint that some deeper physical mechanism is at work. That is, either some previously unknown symmetry is protecting the Higgs mass or the cutoff scale is order(TeV).

@@

    \fxnote{Clarify that not technically a problem. Nature might just be that way. Anthropic principle almost like an attempt to restore naturalness to a universe that appears unnatural, says Andrew} There are three main approaches to the apparently unnatural Higgs mass\fxnote{specify}: (1) argue that it was never really a problem in the first place, (2) reduce the SM cutoff scale, and (3) introduce a new symmetry to protect the Higgs mass. Arguments against naturalness often involve the anthropic principle, which claims that it should come as no surprise that humans live in a universe whose fundamental parameters are tuned to produce carbon-based life. Alternatively, some theories, such as large extra dimensions, lower the SM cutoff by proposing that gravity is spread across more than 3 spatial dimensions, which lowers the Planck mass itself. Finally, the dominant BSM theory that aims to solve the naturalness problem by introducing a new symmetry is supersymmetry, which is explained below.

@@

    In SUSY models, LLPs arise for the same basic reasons, and different SUSY models produce LLPs in different ways. The most straightforward SUSY LLP occurs in models with conserved R-partity, a proposed symmetry that prevents proton decay\fxnote{Be prepared to show this. Maybe add some diagrams illustrating proton decay w/o R-parity}. In models with R-parity, the SM particles are assigned R-parity +1 and their superpartners are assigned R-parity -1. Conserving the product of R-parity at each vertex has two immediate phenomenalogical consequences: (1) sparticles can only be produced in pairs and (2) the lightest supersymmetric particle (LSP) is absolutely stable. A neutral LSP could show up in collider searches as missing energy (MET), making MET a key signature in many conventional searches.

@@

\section{The CMS Detector}\fxnote{Add pictures of everything}
\subsection{Overview}
    \fxnote{Add LHC description}  
    \fxnote{Mention that ATLAS is similar}  
    \fxnote{Maybe mention PDFs. Definitely know about them}  
    \fxnote{cite cms experiment at the cern lhc}
    The Compact Muon Solenoid (CMS) detector is designed to reconstruct a variety of particles from 14 TeV\fxnote{Mention lower-energy runs} proton-proton collisions at the Large Hadron Collider (LHC). To meet this goal, CMS combines information from several subdetectors nested radially in and around a 4-T superconducting solenoid. All together, CMS is 21.6 m long, 14.6 m across, and weighs approximately 12500 tons. The subdetectors that make up CMS are described below.

\subsection{Tracker}
    \fxnote{cite CMS TDR, jinst 12 c02033}
    \fxnote{what about readout, cooling, etc?}
    \fxnote{mention that analyses below used pre-upgrade tracker}
    \fxnote{mention stereo modules and be able to explain stereo modules}
    In the region closest to the interaction point, CMS uses a fast, high-granularity silicon tracker to reconstruct tracks and pinpoint primary and secondary vertices.\fxnote{out-of-fielder may not know about 'track' or 'vertex'} The tracker is subdivided into two regions: at r $<$ 20 cm, the high particle flux \fxnote{specify} requires small pixels to keep occupancy near 0.1\%. Moving farther from the IP decreases particle flux, which allows the use of larger silicon strips.

    The pixel tracker, which was upgraded in winter 2016/17, makes up the innermost layer and features approximately 124 million silicon pixels, each of which covers an active area of 100 by 150 $um^2$. The pixels are spread between four barrel layers (BPIX) at 2.9 $<$ r $<$ 16 cm and 3 endcap rings\fxnote{Andrew says it's 'disc', not 'ring'. Each disc is composed of two concentric rings of modules} (FPIX) at 29 $<$ z $<$ 52 cm. The upgraded pixel tracker should provide 4-hit tracking out to eta $<$ 2.4 and improved b-tagging over the original pixel tracker despite the increased pileup expected in 2017.

    Just outside the pixel tracker, the silicon strip tracker (SST) occupies the 20 $<$ r $<$ 116 cm and $|z|$ $<$ 282 cm region of CMS. Composed of 9.3 million silicon strips that vary from \_ to \_ in size \fxnote{look up} depending on particle flux in the region, the SST covers an active area of roughly 196 $m^2$. At each trigger, the strip output voltage is read out via optical link.

\subsection{Electromagnetic Calorimeter}
    \fxnote{cite CMS TDR}
    \fxnote{talk about readout?}
    \fxnote{More in the way of concept/how stuff works?}
    After traversing the inner tracker, a particle would next encounter the electromagnetic calorimeter (ECAL). As a homogeneous scintillation calorimeter, ECAL uses 61200 lead tunstate crystals in the barrel and 7324 in each endcap to reconstruct the energy deposited during electromagnetic showers. Lead tungstate crystals allow for a fast (80\% of light within 25 ns), compact (radiation length = 0.89 cm), fine-grained (Moliere\fxnote{Andrew says 'radius', not 'length', and use accent!} length = 2.2 cm), and radiation hard (up to 10 Mrad\fxnote{learn context for this number}) calorimeter. The main drawback is the relatively low light yield (30 photon / MeV), which necesitates photodetectors with intrinsic gain that work in magnetic fields \fxnote{say B-field part better}.

    The barrel section (EB) extends radially from 129 to 177 \fxnote{look up} cm and covers a pseudorapidity\fxnote{define} range of 0 to 1.479. The crystals are tapered to approximately project back to the IP but not so perfectly that likely particle trajectories align with cracks. Each crystal is approximately one Moliere radius wide and 25.8 radiation lengths deep.

    The crystals in each endcap section (EE) are arranged in an x-y grid that starts at $|z|$ = 315 cm and covers a pseudorapidity range of 1.479 to 3.0. Additionally, a preshower detector, which consists of two planes of silicon strip detectors and a lead absorber, sits just inside the grid of lead tungstate crystals. \fxnote{Say what the preshower is for? Is it for pi0 rejection? If so, how and why?}

\subsection{Hadronic Calorimeter}
    \fxnote{cite CMS TDR}
    \fxnote{talk about readout?}
    The hadronic calorimeter (HCAL) uses 3.7mm plates of plastic scintillator interspersed within brass absorber to reconstruct the energy deposited during hadronic showers. Embedded wavelength-shifting fibers capture the scintillation light and transfer it to clear fibers so it can eventually be read out by hybrid photodiodes.

    The barrel section (HB) spans a pseudorapidty range of -1.4 to 1.4 and has 2304 towers \fxnote{check}, each of which contains 14 \fxnote{check} brass plates and covers an area of 0.087 x 0.087 in eta-phi \fxnote{get a feel for this area}. In addition, an extra layer (or two at eta = 0) of scintillator tiles sits just outside the solenoid. This extra layer, known as hadron outer (HO), spans a pseudorapidty range of -1.26 to 1.26 and increases the minimum effective HCAL interaction length to greater than 11.8.

    Each endcap spans a pseudorapidity range of 1.3 to 3.0 with 14 towers in eta and 5 to 10 degree phi segmentation. Also, a steel and quartz fiber forward calorimeter (HF) sits 11.2 m from the interaction pipe in a pseudorapidty range of 3.0 to 5.0. In HF, particles produce Cherenkov light when traversing the quartz fibers that run parallel to the beamline. \fxnote{say why HF is useful or mention crazy flux?}

\subsection{Solenoid}
    \fxnote{cite cms experiment at the cern lhc}
    CMS employs a 4 T superconducting solenoid to aid in the measurement of charged particle momenta. The solenoid consists of 2168 turns of Nb-Ti superconducting cable and has an inner diameter of 6 m and a length of 12.5 m. The flux returns through an iron yoke that also houses the muon system. The significant \fxnote{quantify?} bending power helps CMS meet its physics goals of unambiguous sign determination and momentum resolution of 10\% for muons up to 1 TeV.

\subsection{Muon System}
    \fxnote{cite CMS TDR}
    \fxnote{Specifically mention CMS design specs to meet physics goals?}
    The muon system (MS), which is the outermost subdetector, detects muons with 3 varieties of gaseous ionization detectors: drift tubes (DTs) in the barrel, cathode strip chambers (CSCs) in the endcaps, and resistive plate chambers (RPCs) in both the barrel and endcaps. The choice of detector varies between barrel and endcap due to the difference in neutron-induced background, muon rates, and magnetic field strength. The RPCs are useful in the endcaps and barrel because their fast response and good time resolution allow unambiguous bunch crossing identification. Combining MS and tracker measurements improves the muon pT\fxnote{define} resolution at high momenta where the tracker pT resolution declines \fxnote{quantify or show std plot?}.

    In the barrel detector (BD), four layers of DTs and and RPCs are embedded in the solenoid return yoke at 4.0, 4.9, 5.9, and 7.9 m. \fxnote{Say how DT works?} The maximum drift length is 2 cm and the single point resolution is 200 um. When reconstructing a vector describing the muon momentum, the phi precision is better than 100 um in position and 1 mrad in direction.

    Each muon endcap detector (ME) is composed of 234 CSCs and 4 RPC stations \fxnote{figure out exactly what RPC station means and say that instead}. Each CSC has six gas gaps with radial cathode strips and nearly perpendicualar planes of anode wires. The wire signal from the ionization-induced electron avalanch is fast enough to use in the L1 trigger, while the slower \fxnote{quantify} cathode strip signal provides precise \fxnote{quantify} position measurements. All in all, the CSC spacial resolution is approximately 200 um and the angular resolution is approximately 10 mrad.

\subsection{Trigger}
    \fxnote{cite CMS TDR, jinst 12 c03021}
    \fxnote{Is entire detector read out at L1?}
    \fxnote{Mention fpgas in L1 or more details about HLT?}
    \fxnote{Sloppy, but I'm getting tired}
    The trigger reduces the data writing rate from the 40 MHz collision rate to less than 1 kHz so that events can be written to tape. The rate reduction happens in two stages: Level-1 (L1) and High-Level Trigger (HLT). L1 uses input from ECAL, HCAL, and MS that represents physics objects (e/gamma, tau, jets, MET\fxnote{define}, and mu) and uses custom electronics to reduce the rate to $\approx$100 kHz in 3.8 us. The HLT then uses a dedicated processor farm to further reduce the rate to the desired $<$ 1 kHz.

@@

    After estimating 0.02 +- 0.02 background events, exactly 0 are observed. The result is then interpreted as an upper limit on the gluino mass and pair-production cross section as a function of gluino lifetime. For an LSP neutralino mass of 100 GeV, the gluino mass limit is approximately 2000 GeV for lifetimes in the 20 ps to 10 ns range. \fxnote{Include plots}

@@

    In addition to the above criteria, the authors developed a new muon reconstruction algorithm, called displaced standalone (DSA), that uses only muon system hits and does not constrain the location of the primary vertex in any way. The full selection requires exactly one good DSA track in each hemisphere with pT greater than 50 GeV, no reconstructed vertices, and several criteria related to the quality of the reconstructed track and timing measurement. Finally, restrictions on the direction of muon momentum (incoming vs outgoing), relative time measurements, and maximum number of CSC hits (0) minimize background from beam halo and cosmics.

@@

    When building a natural SUSY model, certain constraints are nearly unavoidable\fxnote{Dangerous. What if Linda knows how to avoid them?}. Specifically, the higgsino, which affects mH at tree level; the stop, which affects mH at one loop; and the gluino, which affets mStop at one loop and therefore mH at two, must all be heavy enough to pull mH up to 125 GeV\fxnote{Do I really understand this?} but light enough to avoid excessive fine tuning. Furthermore, the stop and gluino masses are correlated -\fxnote{m-dash?} a large difference between the two would be another source of fine tuning.

>>>>

\usepackage[final]{fixme}
\fxsetup{layout=footnote}
\usepackage[left]{lineno}
\usepackage{amsmath,amsthm,amssymb,mathtools,graphicx,caption,subcaption,mathrsfs,cancel,multirow,enumitem,setspace,sectsty,cite,hyperref,siunitx,cancel}
\usepackage{fullpage}

@@

    All massive particles correct the Higgs mass with terms proportional to $\Lambda^2$. Experimentally, the Higgs mass is \SI{125}{\giga\electronvolt}\fxnote{cite CMS, ATLAS}, a value that must be achieved by the sum of the bare mass and all corrections. Although corrections differ in sign, the precise cancellation of many extremely large terms to produce a value as small as the Higgs mass is extremely unlikely. In fact, the fine-tuning necessary to produce the Higgs mass is on the order of one part in \num{e30} if the SM is valid up to the Plank scale ($\mPlanck\approx$ \SI{e16}{\giga\electronvolt}), where quantum gravity becomes important. While it's possible that the bare mass and corrections just so happen to almost perfectly cancel, such miraculous fine tuning could also be a hint that some deeper physical mechanism is at work. That is, either some previously unknown symmetry is protecting the Higgs mass or the cutoff scale is order(TeV).

@@

    \fxnote{Clarify that not technically a problem. Nature might just be that way. Anthropic principle almost like an attempt to restore naturalness to a universe that appears unnatural, says Andrew} There are three main approaches to the apparently unnatural Higgs mass\fxnote{specify}: (1) argue that it was never really a problem in the first place, (2) reduce the SM cutoff scale, and (3) introduce a new symmetry to protect the Higgs mass. Arguments against naturalness often involve the anthropic principle, which claims that it should come as no surprise that humans live in a universe whose fundamental parameters are tuned to produce carbon-based life. Alternatively, some theories, such as large extra dimensions, lower the SM cutoff by proposing that gravity is spread across more than three spatial dimensions, which lowers the Planck mass itself. Finally, the dominant BSM theory that aims to solve the naturalness problem by introducing a new symmetry is supersymmetry, which is explained below.

@@

    In SUSY models, LLPs arise for the same basic reasons, and different SUSY models produce LLPs in different ways. The most straightforward SUSY LLP occurs in models with conserved R-partity, a proposed symmetry that prevents proton decay\fxnote{Be prepared to show this. Maybe add some diagrams illustrating proton decay w/o R-parity}. In models with R-parity, the SM particles are assigned R-parity +1 and their superpartners are assigned R-parity -1. Conserving the product of R-parity at each vertex has two immediate phenomenalogical consequences: (1) sparticles can only be produced in pairs and (2) the lightest supersymmetric particle (LSP) is absolutely stable. A neutral LSP could show up in collider searches as missing energy ($\MET$), making $\MET$ a key signature in many conventional searches.

@@

\section{The CMS Detector}\fxnote{Add pictures of everything}
\subsection{Overview}
    \fxnote{Add LHC description}  
    \fxnote{define eta, coordinate system in general}  
    \fxnote{Mention that ATLAS is similar}  
    \fxnote{Maybe mention PDFs. Definitely know about them}  
    \fxnote{cite cms experiment at the cern lhc}
    The Compact Muon Solenoid (CMS) detector is designed to reconstruct a variety of particles from proton-proton collisions at the Large Hadron Collider (LHC). To meet this goal, CMS combines information from several subdetectors nested radially in and around a \SI{4}{\tesla} superconducting solenoid. All together, CMS is \SI{21.6}{\m} long, \SI{14.6}{\m} across, and weighs approximately \SI{12500}{t}. The subdetectors that make up CMS are described below.

\subsection{Tracker}
    \fxnote{cite CMS TDR, jinst 12 c02033}
    \fxnote{mention that analyses below used pre-upgrade tracker}
    \fxnote{mention stereo modules and be able to explain stereo modules}
    In the region closest to the interaction point, CMS uses a fast, high-granularity silicon tracker to reconstruct tracks and pinpoint primary and secondary vertices.\fxnote{out-of-fielder may not know about 'track' or 'vertex'} The tracker is subdivided into two regions: at $\mathrm{r}<\SI{20}{cm}$, the high particle flux \fxnote{specify} requires small pixels to keep occupancy near \SI{0.1}{\percent}. Moving farther from the IP decreases particle flux, which allows the use of larger silicon strips.

    The pixel tracker, which was upgraded in winter 2016/17, makes up the innermost layer and features approximately \num{124} million silicon pixels, each of which covers an active area of \num{100} by \SI{150}{\micro\meter^2}. The pixels are spread between four barrel layers (BPix) at $\num{2.9}<\mathrm{r}<\SI{16}{cm}$ and 3 endcap disks (FPix) at $\num{29} < \mathrm{z} < \SI{52}{cm}$. The upgraded pixel tracker should provide 4-hit tracking out to $\eta < \num{2.4}$ and improved b-tagging over the original pixel tracker despite the increased pileup expected in 2017.

    Just outside the pixel tracker, the silicon strip tracker (SST) occupies the $\num{20} < r < \SI{116}{cm}$ and $\lvert z \rvert < \SI{282}{cm}$ region of CMS. Composed of \num{9.3} million silicon strips that vary from \_ to \_ in size \fxnote{look up} depending on particle flux in the region, the SST covers an active area of roughly \SI{196}{m^2}. At each trigger, the strip output voltage is read out via optical link.

\subsection{Electromagnetic Calorimeter}
    \fxnote{cite CMS TDR}
    \fxnote{I define EE & EB but never use those definitions}
    After traversing the inner tracker, particles next encounter the electromagnetic calorimeter (ECAL). As a homogeneous scintillation calorimeter, ECAL uses \num{61200} lead tunstate crystals in the barrel and \num{7324} in each endcap to reconstruct the energy deposited during electromagnetic showers. Lead tungstate crystals allow for a fast (\SI{80}{\percent} of light within \SI{25}{ns}), compact (radiation length = \SI{0.89}{cm}), fine-grained (Moli\`ere radius = \SI{2.2}{cm}), and radiation hard (up to 10 Mrad\fxnote{learn context for this number}) calorimeter. The main drawback is the relatively low light yield (\SI{30}{photon\per\mega\electronvolt}), which necesitates photodetectors with intrinsic gain that work in magnetic fields.

    The barrel section (EB) extends radially from \num{129} to \SI{177}{cm} and covers a pseudorapidity range of \num{0} to \num{1.479}. The crystals are tapered to approximately project back to the IP\fxnote{define if not already} but not so perfectly that likely particle trajectories align with cracks. Each crystal is approximately one Moli\`ere radius wide and 25.8 radiation lengths deep.

    The crystals in each endcap section (EE) are arranged in an x-y grid that starts at $\lvert z \rvert = \SI{315}{cm}$ and covers a pseudorapidity range of \num{1.479} to \num{3.0}. Additionally, a preshower detector, which consists of two planes of silicon strip detectors and a lead absorber, sits just inside the grid of lead tungstate crystals. \fxnote{Say what the preshower is for? Is it for pi0 rejection? If so, how and why?}

\subsection{Hadronic Calorimeter}
    \fxnote{cite CMS TDR}
    \fxnote{define HB & HF never to be used}
    The hadronic calorimeter (HCAL) uses \SI{3.7}{mm} plates of plastic scintillator interspersed within brass absorber to reconstruct the energy deposited during hadronic showers. Embedded wavelength-shifting fibers capture the scintillation light and transfer it to clear fibers to be read out by hybrid photodiodes.

    The barrel section (HB) spans a pseudorapidty range of \num{-1.4} to \num{1.4} and has \num{2304} towers \fxnote{check}, each of which contains \num{14} \fxnote{check} brass plates and covers an area of \num{0.087} x \SI{0.087}{in} $\eta-\phi$ \fxnote{get a feel for this area}. In addition, an extra layer (or two at $\eta = \num{0}$)of scintillator tiles sits just outside the solenoid. This extra layer, known as hadron outer (HO), spans a pseudorapidty range of \num{-1.26} to \num{1.26} and increases the minimum effective HCAL interaction length to greater than \num{11.8}.

    Each endcap spans a pseudorapidity range of \num{1.3} to \num{3.0} with \num{14} towers in eta and \num{5} to \SI{10}{\degree} $\phi$ segmentation. Also, a steel and quartz fiber forward calorimeter (HF) sits \SI{11.2}{m} from the interaction pipe in a pseudorapidty range of \num{3.0} to \num{5.0}. In HF, particles produce Cherenkov light when traversing the quartz fibers that run parallel to the beamline. \fxnote{say why HF is useful or mention crazy flux?}

\subsection{Solenoid}
    \fxnote{cite cms experiment at the cern lhc}
    CMS employs a \SI{4}{T} superconducting solenoid to aid in the measurement of charged particle momenta. The solenoid consists of \num{2168} turns of Nb-Ti superconducting cable and has an inner diameter of \SI{6}{m} and a length of \SI{12.5}{m}. The flux returns through an iron yoke that also houses the muon system. The significant \fxnote{quantify?} bending power helps CMS meet its physics goals of unambiguous sign determination and momentum resolution of \SI{10}{\percent} for muons up to \SI{1}{\tera\electronvolt}.

\subsection{Muon System}
    \fxnote{cite CMS TDR}
    \fxnote{Specifically mention CMS design specs to meet physics goals?}
    The muon system (MS), which is the outermost subdetector, detects muons with \num{3} varieties of gaseous ionization detectors: drift tubes (DTs) in the barrel, cathode strip chambers (CSCs) in the endcaps, and resistive plate chambers (RPCs) in both the barrel and endcaps. The choice of detector varies between barrel and endcap due to the difference in neutron-induced background\fxnote{what?} , muon rates, and magnetic field strength\fxnote{why does B matter?}. The RPCs are useful in the endcaps and barrel because their fast response and good time resolution allow unambiguous bunch crossing identification. Combining MS and tracker measurements improves the muon pT\fxnote{define} resolution at high momenta where the tracker pT resolution declines \fxnote{quantify or show std plot?}.

    In the barrel detector (BD), four layers of DTs and and RPCs are embedded in the solenoid return yoke at \num{4.0}, \num{4.9}, \num{5.9}, and \SI{7.9}{m}. The maximum drift length is \SI{2}{\cm} and the single point resolution is \SI{200}{\cm}. When reconstructing a vector describing the muon momentum, the $\phi$ precision is better than \SI{100}{\micro\m} in position and \SI{1}{\milli\radian} in direction.

    Each muon endcap detector (ME) is composed of \num{234} CSCs and four RPC stations \fxnote{figure out exactly what RPC station means and say that instead}. Each CSC has six gas gaps with radial cathode strips and nearly perpendicualar planes of anode wires. The wire signal from the ionization-induced electron avalanch is fast enough to use in the L1 trigger, while the slower \fxnote{quantify} cathode strip signal provides precise \fxnote{quantify} position measurements. All in all, the CSC spacial resolution is approximately \SI{200}{\micro\m} and the angular resolution is approximately \SI{10}{\milli\radian}.

\subsection{Trigger}
    \fxnote{cite CMS TDR, jinst 12 c03021}
    \fxnote{Is entire detector read out at L1?}
    The trigger reduces the data writing rate from the \SI{40}{\mega\hertz} collision rate to less than \SI{1}{\kilo\hertz} so that events can be written to tape. The rate reduction happens in two stages: Level-1 (L1) and High-Level Trigger (HLT). L1 uses input from ECAL, HCAL, and MS that represents physics objects ($\mathrm{e}$/$\gamma$, $\tau$, jets, $\mu$, and $\MET$) and uses custom electronics to reduce the rate to $\approx$100 kHz in 3.8 us. The HLT then uses a dedicated processor farm to further reduce the rate to the desired $<$ 1 kHz.

@@

    After estimating 0.02 +- 0.02 background events, exactly 0 are observed. The result is then interpreted as an upper limit on the gluino mass and pair-production cross section as a function of gluino lifetime. For an LSP neutralino mass of \SI{100}{\giga\electronvolt}, the gluino mass limit is approximately \SI{2000}{\giga\electronvolt} for lifetimes in the 20 ps to 10 ns range. \fxnote{Include plots}

@@

    In addition to the above criteria, the authors developed a new muon reconstruction algorithm, called displaced standalone (DSA), that uses only muon system hits and does not constrain the location of the primary vertex in any way. The full selection requires exactly one good DSA track in each hemisphere with pT greater than \SI{50}{\giga\electronvolt}, no reconstructed vertices, and several criteria related to the quality of the reconstructed track and timing measurement. Finally, restrictions on the direction of muon momentum (incoming vs outgoing), relative time measurements, and maximum number of CSC hits (0) minimize background from beam halo and cosmics.

@@

    When building a natural SUSY model, certain constraints are nearly unavoidable\fxnote{Dangerous. What if Linda knows how to avoid them?}. Specifically, the higgsino, which affects mH at tree level; the stop, which affects mH at one loop; and the gluino, which affets mStop at one loop and therefore mH at two, must all be heavy enough to pull mH up to \SI{125}{\giga\electronvolt}\fxnote{Do I really understand this?} but light enough to avoid excessive fine tuning. Furthermore, the stop and gluino masses are correlated -\fxnote{m-dash?} a large difference between the two would be another source of fine tuning.
